Named Entity Recognition as Structured Prediction

### 2012-11-11 doc/report/paper.tex
+++

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish and Dutch was taken from the CoNLL Shared Task 2002 \cite{tksintro} and 
the CoNLL Shared Task 2003 \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the data for English and German.
%The ConNLL shared tasks are organized challenges, where the organisers propose a task and provide the participants with the
%training and test data. 
%In 2002 and 2003, the task was Named Entity Recognition. 
In 2002 and 2003 CoNLL shared tasks on Named Entity Recognition, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}.\todo{? hab ich nicht kapiert :D}
Table~\ref{table:Base} shows the baselines for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as BIO-tags that indicate the position of a token in the Named Entity. %put in ``tokenized, chunked''
%Our approach is based on \cite{strlearn}, of the group that won the challenge for Spanish and Dutch in 2002.

@@

In the following, we show the influence of each of the three sets of features on the resulting accuracy.
\FloatBarrier
\begin{figure*}[t!]
 \includegraphics[scale=0.5]{Plot.png}
\end{figure*}

>>>>

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish and Dutch was taken from the CoNLL Shared Task 2002 \cite{tksintro} and 
the CoNLL Shared Task 2003 \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the data for English and German.
%The ConNLL shared tasks are organized challenges, where the organisers propose a task and provide the participants with the
%training and test data. 
%In 2002 and 2003, the task was Named Entity Recognition. 
In 2002 and 2003 CoNLL shared tasks were on Named Entity Recognition. The baseline system first decides on the most frequent Named Entity class C in the training data
and then labels all occurrences of a Named Entity found in the test data with class C regardless of context. 
Any named entities that did not occur in the training data are also not assigned any class in the test data.
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}.\todo{? hab ich nicht kapiert :D}
Table~\ref{table:Base} shows the baselines for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as BIO-tags that indicate the position of a token in the Named Entity. %put in ``tokenized, chunked''
%Our approach is based on \cite{strlearn}, of the group that won the challenge for Spanish and Dutch in 2002.

@@

In the following, we show the influence of each of the three sets of features on the resulting accuracy.
\FloatBarrier
\begin{figure*}[t!]
\centering
 \includegraphics[scale=0.5]{Plot.png}
\end{figure*}
